---
title: "Study 03: Bouncy Castle Evolution and Breaking Changes"
author: "Rodrigo Bonifácio, Stefan Krüger, Krishna Narasimhan, Eric Bodden, and Mira Mezini "
date: "March, 2021"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "images/")
library(reshape2)
library(sqldf)
library(stringr)
setwd(".")
```

## Load the Bouncy Castle API dataset

```{r}
bc <- read.csv("releases.csv", sep=",", head=F)
colnames(bc) <- c("Release", "ClassName", "Abstract", "SuperClass", "Interfaces")
```

## Check the number of implementations for some primitives

In the paper, we report the number of Bouncy Castle implementations 
for the cryptographic primitives Block Cipher, MAC, Message Digest, 
and Stream Cipher. 

```{r}
md <- sqldf("select Release, count(distinct ClassName) as 'MessageDigest' 
       from bc 
       where Interfaces like '%org.bouncycastle.crypto.ExtendedDigest%'
         and Abstract = 'false'     
       group by Release
       order by 2 desc")

mac <- sqldf("select Release, count(distinct ClassName) as MAC 
       from bc 
       where Interfaces like '%org.bouncycastle.crypto.Mac%'
         and Abstract = 'false'     
       group by Release
       order by 2 desc")

blockCipher <- sqldf("select Release, count(distinct ClassName) as 'BlockCipher' 
       from bc 
       where Interfaces like '%org.bouncycastle.crypto.BlockCipher%'
         and Abstract = 'false'     
       group by Release
       order by 2 desc")

streamCipher <- sqldf("select Release, count(distinct ClassName) as 'StreamCipher' 
       from bc 
       where Interfaces like '%org.bouncycastle.crypto.StreamCipher%'
         and Abstract = 'false'     
       group by Release
       order by 2 desc")

all <- merge(md, mac)
all <- merge(all, blockCipher)
all <- merge(all, streamCipher)

all$Release <- gsub("jdk15-", "", all$Release)
# all$Release <- as.factor(all$Release)
```

   * Detail the number of cryptographic implementations 
   
```{r}
all 
```

   * Generate the plot in the paper's Figure 7
   
```{r}
plot(all$Release, all$MessageDigest,  type = "o", frame = FALSE, pch = 19, 
     col = "blue", xlab="Release", ylab="Algorithm Implementations", 
     ylim=c(0,50), cex.lab=0.7, cex.axis=0.7)

lines(all$Release, all$MAC, type = "o", pch=18, col="blue3")
lines(all$Release, all$BlockCipher, type = "o", pch=17, col="blue4")
lines(all$Release, all$StreamCipher, type="o", pch=16, col="darkblue")
```

## Load the Bouncy Castle dataset of breaking changes

```{r load}
bc <- read.csv("bc.csv", head=T, sep=";")
bc <- melt(bc, id.vars=c("Change"), variable.name="Release", value.name="Total")
colnames(bc)
```

## Generate the plot summarizing the bouncy castle braking changes

```{r plot}
bcc <- sqldf("select Change, sum(Total) as Total from bc group by Change")
bcc <- bcc[order(-bcc$Total), ]
barplot(bcc$Total, col=topo.colors(11), ylim=c(0,1200))
legend("topright", title="Changes", fill=topo.colors(11), legend=bcc$Change, cex = 0.8)
```
