---
title: "Study 03: Android Crypto Violation Analysis"
author: "Rodrigo Bonifácio, Stefan Krüger, Krishna Narasimhan, Eric Bodden, and Mira Mezini "
date: "March, 2021"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(sqldf)
require(xtable)
setwd(".")
```

## Load the datasets

We have a total of 9 + 1 datasets

   * One dataset of violations for each one of the 9 configurations used in the study
   * One dataset with the specification of the Android apps used in the study


```{r load}
android_0108 <- read.csv("android-0108.csv", head=F, sep=";")
android_0116 <- read.csv("android-0116.csv", head=F, sep=";")
android_25plus <- read.csv("android-25plus.csv", head=F, sep=";")

android_bsi_0108 <- read.csv("android-bsi-0108.csv", head=F, sep=";")
android_bsi_0116 <- read.csv("android-bsi-0116.csv", head=F, sep=";")
android_bsi_25plus <- read.csv("android-bsi-25plus.csv", head=F, sep=";")

android_cc_0108 <- read.csv("android-cc-0108.csv", head=F, sep=";")
android_cc_0116 <- read.csv("android-cc-0116.csv", head=F, sep=";")
android_cc_25plus <- read.csv("android-cc-25plus.csv", head=F, sep=";")

apps <- read.csv("apps.csv")
```

## Rename the datasets' columns 

```{r rename}

colnames(android_0108) <- c("configuration", "project_name", "clasz", "class_name", "algorithm", "expected", "full_description") 
colnames(android_0116) <- c("configuration", "project_name", "clasz","class_name", "algorithm", "expected", "full_description") 
colnames(android_25plus) <- c("configuration", "project_name", "clasz","class_name", "algorithm", "expected", "full_description") 
colnames(android_bsi_0108) <- c("configuration", "project_name", "clasz","class_name", "algorithm", "expected", "full_description") 
colnames(android_bsi_0116) <- c("configuration", "project_name", "clasz","class_name", "algorithm", "expected", "full_description") 
colnames(android_bsi_25plus) <- c("configuration", "project_name", "clasz","class_name", "algorithm", "expected", "full_description") 
colnames(android_cc_0108) <- c("configuration", "project_name", "clasz","class_name", "algorithm", "expected", "full_description") 
colnames(android_cc_0116) <- c("configuration", "project_name", "clasz","class_name", "algorithm", "expected", "full_description") 
colnames(android_cc_25plus) <- c("configuration", "project_name", "clasz","class_name", "algorithm", "expected", "full_description") 
```

## Join the datasets of violations

```{r joining}
violations <- rbind(android_0108, android_0116)
violations <- rbind(violations, android_25plus)
violations <- rbind(violations, android_bsi_0108)
violations <- rbind(violations, android_bsi_0116)
violations <- rbind(violations, android_bsi_25plus)
violations <- rbind(violations, android_cc_0108)
violations <- rbind(violations, android_cc_0116)
violations <- rbind(violations, android_cc_25plus)
```

## Number of rows in the `violations` and `apps` datasets

```{r}
nrow(violations)
nrow(apps)
```

## Remove from the analysis apps with less than 9 configurations

```{r}
apps <- sqldf("select SoftwareId, Configurations 
                   from apps 
                   where Configurations = 9")
nrow(apps)

apps["project_name"] <- gsub(".apk", "", apps$SoftwareId)
apps["project_name"] <- gsub("/home/amluis/cryptoAnalysis/AndroidZooApps/", "", apps$project_name)
```

## Join the `violations` and `apps` datasets

```{r}
df <- sqldf("select *
             from violations
             where project_name in 
             (select project_name from apps)")
```

## Summarize the number of violations

### Considering all violations 
```{r}
sqldf("select configuration, count(distinct project_name)
      from violations 
      group by configuration")
```

### Considering all violations not related to `SHA256withECDSA` (a false positive)


```{r}
sqldf("select configuration, count(distinct project_name) 
      from violations 
      where algorithm != 'SHA256withECDSA'
      group by configuration")
```

### Considering all violations, though discarding common libraries (from Google and Facebook)

```{r}

t1 <- sqldf("select configuration, count(distinct project_name) as apps, count(*) violations
      from violations 
      where algorithm != 'SHA256withECDSA' 
         and not (class_name like '%MessageDigest' 
                  and full_description like '%Third parameter (with value 0)%') 
         and clasz not like 'com.google.android.gms%' 
         and clasz not like 'com.facebook.ads%' 
         and clasz not like 'com.unity3d%' and 
         clasz not like 'com.android.%'
      group by configuration")

t1["rate"] <- t1$apps * 100 / 6714  

sqldf('select configuration, 6714, apps, rate, violations from t1')

xtable(sqldf('select configuration, 6714, apps, rate, violations from t1'))
```
